---
title: "Weekly Report"
author: "Kudla Fund"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### `r format(Sys.time(), '%B %d %Y')`

The following analysis was conducted for winter, spring, and summer, 2018, starting from 01/02/`r format(Sys.time(), '%Y')` until `r format(Sys.time(), '%m/%d/%Y')`. 13-week treasury bill index was used as a proxy for interest rates (^IRX). Market movements were estimated using S&P 500 index (^GSPC). Financial data was retrieved from Yahoo! finance. 

Over `r as.Date(format(Sys.time(), '%m/%d/%Y'), format = '%m/%d/%Y') - as.Date(paste("01/02/",format(Sys.time(), '%Y')), format = '%m/%d/%Y')` trading days, the fund managed to bring a total return of `r library(zoo); coredata(returns)[1]*100`%, compared to the S&P 500 index of `r library(zoo); SP500_AnnualReturn*100`%. We achieved an annualized Sharpe ratio of `r SharpeRatio`, which is significantly higher than market Sharpe ratio for the same period, `r SP500_Sharpe`.

Our portfolio's beta was `r beta[1][1] `. Maximum drawdown was calculated to be ----%. Further information are provided in the following table and graphs.

```{r echo=FALSE, results='asis'}

library(knitr)
vals = matrix(nrow=3, ncol=2)
vals[1,1] = SP500_Sharpe
vals[1,2] = SharpeRatio
vals[2,1] = SP500_Volatility
vals[2,2] = volatility
vals[3,1] = SP500_AnnualReturn
vals[3,2] = coredata(returns)[1]
rownames(vals) <- c("Sharpe Ratio", "Annualized Volatility", "YTD Return")
colnames(vals) <- c("SP500", "Portfolio")
kable(vals, caption = "Portfolio Values")
```

# Returns Distribution

```{r Returns Distribution, echo=FALSE}
  qplot(CalculateDailyReturns(portfolio) * 100, geom = 'histogram', binwidth = .1) + xlab('Portfolio Returns Distribution (%)') +
    # Create normal curve, adjusting for number of observations and binwidth
    stat_function( 
      fun = function(x, mean, sd, n, bw){ 
        dnorm(x = x, mean = mean, sd = sd) * n * bw
      }, 
      args = c(mean = mean(CalculateDailyReturns(portfolio) * 100), sd = sd(CalculateDailyReturns(portfolio) * 100), n = length(CalculateDailyReturns(portfolio) * 100), bw = 0.1))
```

# Portfolio Value

```{r Portfolio Value, echo=FALSE}

plot(portValue)
```

#Frontier Analysis Graph
```{r Frontier Analysis Graph, echo=FALSE}
  EfficientPortfolio(portfolio)

```
